---
title: "Execution"
author: "Silpa Velagapudi"
date: "January 15, 2020"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    highlight: espresso
    number_sections: true
    latex_engine: xelatex
    fig_width: 7
    fig_height: 8.5
    fig_caption: true
fontsize: 13pt
---

\begin{enumerate}
\item Introduction
\item Data Extraction
\item Creating key field values
\item In-depth Analysis of the Data
\item Conclusion
\end{enumerate}


\pagebreak

1. **Introduction**:

Analysing 1000 NGAX defects created. Trying to find what kind of defects are more frequent during the course of time. 


2. **Data Extraction**:
**Pre-requisites: Loading Packages and Libraries**

First, we load all the necessary packages and libraries.

```{r packages, echo=FALSE, warning=FALSE}
if(!require(dplyr)) install.packages("dplyr", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")



library(dplyr)
library(tidyverse)

```

Downloaded the defects from the Jira Portal and created new file with the required fields and viewing the first 6 records of the file.

```{r inputfilereading, echo=FALSE}

df_exrp <- read_csv("./Data_files/Execution report.csv")
head(df_exrp)
```
```{r executionreport, echo=FALSE}
num <-df_exrp %>% filter(Version=="Staging" & ExecutionStatus %in% c("FAIL","BLOCKED")) %>% group_by(CycleName,ExecutionStatus) %>% summarize(count_key=n()) %>% select(CycleName,ExecutionStatus,count_key)
head(num)
num %>% ggplot(aes(CycleName,count_key)) +  geom_bar(stat="identity",fill="darkseagreen") + geom_text(aes(label = count_key), size = 3) +
  coord_flip() + theme(axis.text.y = element_text(size = 8)) +
  xlab("")
```
```{r}
df_exrp_updated <- df_exrp %>% filter(Version=="Staging" & ExecutionStatus %in% c("FAIL","BLOCKED")) %>% arrange(`Issue Key`) %>% select(CycleName,`Issue Key`,Version,Component,Priority,`Executed On`, ExecutionStatus)
dat <- unique.data.frame(df_exrp_updated)
dat %>% group_by(`Issue Key`)  %>% summarize(count_key=n()) %>% arrange(desc(count_key))
```


